---
title: "Title Data Essay"
subtitle: "Data mining project"
author: 
  - "Zoe von Allmen, zoe.vonallmen@stud.unilu.ch, 12-124-433"
  - "Supervisor: Dr. Andrea De Angelis"
date: today
date-format: "D. MMMM YYYY"
format: 
  pdf:
    documentclass: scrreprt
    number-sections: true
    toc: false
fontsize: 12pt
linestretch: 1.5
geometry: left=2.5cm,right=2.5cm,top=3cm,bottom=3cm
execute:
  echo: false
  warning: false
knitr:
  opts_chunk:
    message: false
editor: 
  markdown: 
    wrap: 72
---

# Introduction

This paper investigates how immigration is discussed in Swiss media,
specifically in the context of national initiatives and referendums.
Using large-scale newspaper data and employing large language models for
classification tasks, the project analyzes how immigration is framed,
the emotional tone applied to it, and whether oppositional constructions
("us" vs. "them") are present. It focuses media discourses during
moments when political stakes were especially high, which is, during
direct democratic votes, and examines how immigration is discussed by
ideologically differing newspapers.

Building on established literature, the basis of this project is the
assumption, that media plays an important role in the perception of
diverse issues. That is not only through what they cover, but how they
do so. through the use of certain linguistic concepts or the
accentuation of certain aspects. Prior research has shown that media
ownership and political orientation can influence the visibility and
framing of certain topics. In Western Europe, and Switzerland in
particular, immigration has become an increasingly salient and
politicized issue. Over the past two decades, Switzerland has held
numerous initiatives and referendums directly addressing immigration,
such as for example the "Masseneinwanderungsinitiative" (Massimmigration
Initiative) in 2014 or the "Begrenzungsinitiative" (Restriction
Initiative) in 2020. Most recently, the "Swiss People's Party" (SVP)
launched a new initiative, called "Nachhaltigkeitsinitiative", which
again addresses the topic of Swiss immigration.

In a direct democratic country like Switzerland, media discourse is
particularly relevant. As the Swiss people vote directly on these
initiatives, public narratives, influenced by media consumption, can
influence perceptions of migrants and even possibly influence policy
support. This project further seeks to expand the discourse analysis by
utilizing the recent advances in large language models to scale up what
has traditionally been small-scale qualitative work. Features such as
framing, sentiment, and opposition, which have often been identified
manually before, are now extracted in a more systematic and large-scale
way.

In summary, this project aims to analyze media discourse of
ideologically different media outlets at times where immigration is
especially politicized and stakes are high - during the time of
initiatives. The study therefor tries to answer the following research
question: *How is immigration represented in Swiss media coverage during
politically salient moments?*

More precisely, the following sub-questions should be answered:

-   *What framing strategies and sentiments are used to define
    immigration and its implications in Swiss media during national
    initiatives?*

-   *To what extent are oppositions constructed or reinforced in
    immigration coverage*

-   *How does the use of these concepts vary across ideologically
    diverse newspapers?*

# Theory

The theoretical basis for this project include framing theory, political
communication and media and the construction of oppositiional
identities. 

1. Framing and Media Representations
Framing theory explains how media influence perception by emphasizing certain aspects of an issue. Entman (1993) defines framing as selecting and emphasizing specific elements of reality to promote a particular interpretation. Immigration is often framed through economic, cultural, security, or humanitarian lenses (Eberl et al., 2018). Reporting can also vary in emotional tomes, such as fear or sympathy, which further shape public opinion (Nabi, 2003). 

2. Media, Ideology, and Direct Democracy
In Switzerland’s system of direct democracy, media plays a crucial role in shaping public debates around referendums and initiatives. Newspapers can act both as agenda-setters (McCombs & Shaw, 1972) and interpreters of political conflict. Research shows that ideological orientation and media ownership affect how issues like immigration are covered (Spirig, 2024; Strömbäck, 2008). During initiatives, when political stakes are high, media framing may help legitimize or challenge particular positions.

3. Identity and Oppositional Framing
Finally, this project draws on discourse theory to analyze how media construct boundaries between “us” (the Swiss) and “them” (immigrants). 


# Data & Method

## Article collection

Relevant newspaper articles were collected via the Swissdox API, which
provides a wide range of Swiss news outlets. The sample collected
contains only articles written in the german language.

Selection criteria included:

*Keyword filtering**: Articles were retrieved based on keyword searches
intended to capture wide range of immigration-related articles. The
final list of keywords included: einwander\* zuwander\* asyl\*
flüchtling\* Personenfreizügigkeit, überfremdung, migrationspolitik,
migrationsabkommen, abschiebung, integrationspolitik These kewords were
selected after initial testing and revising of sample articles to
minimize irrelevant results.

*Newspapers*: Seven major Swiss newspapers were selected to represent a
range of ideological orientations:

-   Basler Zeitung (BAZ) - right wing after ownership changed in 2000?

-   Blick - tabloid

-   Wochenzeitung (WOZ): left-wing

-   Weltwoche (WEW): right wing

-   SRF: public boradcaster, politically neutral

-   Neue Zürcher Zeitung (NZZ): economically liberal/rather conservative

-   Tagesanzeiger (TA) - centrist Only print versions of each newspaper
    were used to avoid duplicates and ensure consistent article
    structure over time, as some articles were retrieved from the early
    2000's.

*Time frames*: To focus on moments of increased politicization, four
Swiss initiatives related to immigration were selected. For each
initiative, a four week time period was defined, three weeks before and
one week after the respective vote. The initiatives include the
following:

-   "Initiative für eine Regelung der Zuwanderung" (Initiative for
    regulating immigration), vote on 24.09.2001, time frame: 2000-06-24
    to: 2000-10-24

-   "Initiative gege Masseneinwanderung" (Initiative against
    massimmigration), vote on 09.02.2014, time frame : 2013-11-09 to:
    2014-03-09

-   Initiative "Stop Überbevölkerung" (Stop overpopulation), vote on
    30.11.2014, time frame: 2014-08-30 to: 2014-12-30

-   "Begrenzungsinitiative" (Restriction initiative), vote on
    27.09.2020, time frame: 2020-06-27 to: 2020-10-27

In total, the final sample based on these filters contained 1731
articles.

## Classification via GPT API

To analyze the articles, the OpenAI GPT-4.0 API was used to perform
classification tasks. The classifications was based on a custom prompt
that defined five separate tasks. Each article was sent into the model
in full text, with a detailed instruction. The full version of the
prompt can be found in the appendix.

**Task Overview** Each article was coded along five dimensions:

Task 1- Relevance: \
Binary classification: \
1: Relevant — the article discusses immigration in the Swiss context. \
0: Not relevant — immigration is not discussed meaningfully, or only in
a foreign/non-Swiss context.

Task 2 - Indirect Mention of Immigration \
Binary classification: \
1: Immigration is mentioned briefly or indirectly, but is not the main
topic. \
0: Either immigration is not mentioned at all, or immigration is the
main topic.

Task 3 - Framing of Immigration \
1: Economic \
2: Cultural/Identity \
3: Security \
4: Humanitarian\
5: Political/Legal\
0: not applicable In the final evaluation, categories 3 (security), 4
(humanitarian) and 0(not applicable) were collapsed into a new label "9
= other", due to their low frequency.

Task 4 - Sentiment Towards Immigration \
1: Hopeful. \
2: Sympathetic. \
3: Neutral. \
4: Concerned / Uncertain. \
5: Fearful. \
6: Angry. \
7: Dismissive / Downplaying. \
For the analysis, due to the low frequencies of some frames, categories
were recoded as follows: \
Sentiment 1 (hopeful) and sentiment 2 (sympathetic) were merged into a
category "8 - positive". \
Sentiments 5 (fearful), 7 (dismissive) and 0 (not applicable) were
collapsed into a new category "9 - other".

Task 5 - Constructed Opposition \
1: An opposition is present. \
0: No opposition is present.

Each task included definitions, a more detailed explanation of the
categories as well as example sentences and categorizations. Further,
the GPT model was instructed to act as an expert on Swiss politics,
political communication and media discourse. Several test runs and
prompt refinements based on the test runs were conducted before
processing the full data set, to ensure the validity and consistency of
the classification. For example, explanations were modified and examples
of edge cases were added. After multiple test runs and quality checks,
the full data set was processed.

Categorization based on...

**Final Sample**: Out of the initial 1731 articles, 706 could not be
classified by the API. Of the remaining 1025 articles, the relevance
task (Task 1) identified 772 articles as relevant for the research
question. These 772 articles comprise the final data set which was used
for the analysis.

## Results

```{r, echo=FALSE, results='hide'}
library(tidyverse)
Joined_Data_filtered <- read_csv("Data/analysis_data_relevant_only.csv")
nrow(Joined_Data_filtered)

Joined_Data_filtered |> 
  select(medium_name) |> 
  map(table)
```

The final data set consists of 772 articles. This includes 169 articles
of the Basler Zeitung (BAZ), 175 articles of the Tages-Anzeiger (TA),
172 articles of the Neue Zürcher Zeitung (NZZ), 124 articles of SRF, 68
articles of Blick, 53 articles of Die Weltwoche and 15 articles of the
WOZ.

## Analysis of frames

```{r, echo=FALSE, results='hide'}
Joined_Data_filtered <- Joined_Data_filtered |>
  mutate(code_3_numeric = as.numeric(as.character(code_3))) |>
  mutate(task3_collapsed = case_when(
    code_3_numeric %in% c(0, 3, 4) ~ 9,
    TRUE ~ code_3_numeric
  ))

Joined_Data_filtered <- Joined_Data_filtered |>
  mutate(task3_collapsed = as.factor(task3_collapsed))

library(nnet)
m_frames_medium <- multinom(task3_collapsed ~ medium_name, data = Joined_Data_filtered)
summary(m_frames_medium)

library(ggeffects)
pred_frame <- ggpredict(m_frames_medium, terms = "medium_name")

Pred_Frame <- plot(pred_frame) +
  ggtitle("Predicted Probabilities of Frame") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

To examine the newspaper's use of different frames a multinominal
logictic regression was conducted, with the reference category economic
frame (frame 1). Key results are as follows: - Some outlets showed
higher odds of using cultural frames over economic ones. For example,
Die Wochenzeitung and Die Weltwoche had positive coefficients for this
comparison (1.13 and 0.72 respectively), suggesting these outlets are
more likely to frame immigration culturally than economically. - SRF and
Neue Zürcher Zeitung (NZZ) had positive coefficients, indicating they
are more likely to use a political/legal frame than an economic one,
particularly SRF (coefficient = 1.07). - The model suggests a reasonable
model fit (Residual Deviance = 1020.71, AIC = 1062.71), however standard
errors for most coefficients are very large, which suggests that they
may not be statistically significant.

The following visualization shows the predicted probabilities of frames
by newspaper.

```{r, echo=FALSE}
print(Pred_Frame)
```

## Analysis of sentiment

```{r, echo=FALSE, results='hide'}
Joined_Data_filtered |> 
  count(code_4)

Joined_Data_filtered |> 
  group_by(medium_name, code_3) |> 
  summarise(n = n()) |> 
  ungroup()

Joined_Data_filtered <- Joined_Data_filtered |>
  mutate(code_4_numeric = as.numeric(as.character(code_4))) |>
  mutate(task4_collapsed = case_when(
    code_4_numeric %in% c(1, 2) ~ 8, #hopeful & sympathetic => positive
    code_4_numeric %in% c(0, 5, 7) ~ 9, #not applicable, fearful, dismissive => other
    TRUE ~ code_4_numeric
  ))

Joined_Data_filtered <- Joined_Data_filtered |>
  mutate(task4_collapsed = as.factor(task4_collapsed))

m_sentiment_medium <- multinom(task4_collapsed ~ medium_name, data = Joined_Data_filtered)
summary(m_sentiment_medium)

#Predicted sentiment
library(ggeffects)
pred_sentiment <- ggpredict(m_sentiment_medium, terms = "medium_name")

Pred_Sentiment <- plot(pred_sentiment) +
  ggtitle("Predicted Probabilities of Sentiment") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

To assess how the newspapers differ in sentiment used when discussing
immigration, a multinominal logistic regression was run, with sentiment
type as outcome and media outlet as predictor. The neutral tone acts as
reference category. Key results are as follows: - Most media outlets did
not show strong deviations from neutrality. However, Die Wochenzeitung
had a positive coefficient (1.30), suggesting that compared to neutral
tone, it was more likely to use a concerned tone. - Die Weltwoche and
Die Wochenzeitung had relatively strong positive coefficients (1.42 and
2.20), suggesting these outlets may use more emotionally critical or
accusatory language than others. SRF and NZZ, in contrast, had negative
coefficients, indicating they were less likely to express anger relative
to a neutral tone. - Strong negative coefficients for Blick (–13.58) and
Weltwoche (–12.48) indicate that positive sentiment was very unlikely in
these outlets. Die Wochenzeitung stands out with a positive coefficient
(2.31), indicating they used a rather hopeful or sympathetic tone. -
However, some sentiment categories were underrepresented in the data
set, eading to extreme or unstable coefficiets for certain outlets.
esults should be interpreted with caution.

The following visualization shows the predicted probabilities of
sentiment by newspaper.

```{r, echo=FALSE}
print(Pred_Sentiment)
```

## Analysis of constructed oppositions

```{r, echo=FALSE, results='hide'}
Joined_Data_filtered |> 
  count(code_5)

Joined_Data_filtered |> 
  group_by(medium_name, code_5) |> 
  summarise(n = n()) |> 
  ungroup()

Joined_Data_filtered <- Joined_Data_filtered |> 
  mutate(code_5 = as.factor(code_5))

m_opposition_medium <- glm(code_5 ~ medium_name, 
                           data = Joined_Data_filtered, 
                           family = binomial)

summary(m_opposition_medium)

pred_opposition <- ggpredict(m_opposition_medium, terms = "medium_name")
Pred_Opposition <- plot(pred_opposition) +
  ggtitle("Predicted Probability of Constructed Opposition by Media Outlet") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

To examines the presence and variation of constructed oppositions, a
binary logistic regression was run. Constructed opposition (code_5) acts
as the dependent variable, the newspapers as the predictor. Some key
results are as follows: - Die Weltwoche shows a significantly higher
likelihood of constructing oppositions compared to the baseline (B =
1.10, p \< 0.001), suggesting a stronger tendency to emphasize divides
between "the Swiss" and migrants. - Die Wochenzeitung also had a
significantly higher probability (B = 1.27, p \< 0.05), though this
result should be interpreted cautiously due to a smaller sample size. -
In contrast, Neue Zürcher Zeitung was less likely to have oppositional
framing present (B = -0.54, p = 0.049). - The remaining outlets,
including Blick, Tages-Anzeiger, and SRF, did not show statistically
significant deviations from the baseline.

The following visualization shows the predicted probabilities of
constructed opposition by newspaper.

```{r, echo=FALSE}
print(Pred_Opposition)
```

## Conclusion

This project examined how Swiss newspapers represent immigration in the
context of politically salient moments, specifically during national
initiatives and referendums. Based on the results of the analysis, the
research questions are discussed and answered as follows. \
Political ad economic frames dominate the newspapers when it comes to
immigration. Right-leaning newspapers, like Die Weltwoche, are more
frequently employ opositional or cultural farmings, while liberal or
centrist outlets(NZZ, SRF), focus on more on political or legal aspects.
\
Emotional tone, overall, is mostly neutral or concerned, although there
were traces of anger and dismissiveness found. The right-wing newspaper
Die Weltwoche, for example, appears more likely to express an angry
sentiment, while the left-wing newspaper Die Wochenzeitung uses positive
sentiments. \
The use of constructed oppositions, "us vs. them", is not uniform across
the media landscape, Die Weltwoche and Die Wochenzeitung showed higher
likelihoods of constructing such contrasts. \
These findings suggest that even within a non-polarized media
environment like Switzerland, ideological positioning influences how
immigration is framed, especially during times of heightened public
attention and direct democratic decision-making.

## Limitations

Despite these insights, several limitations affect the generalizability
and validity of the findings. First of all, the use of the LLM for for
the article classification introduced some constraints. The
classification of the articles resulted in a substantial proportion of
articles that couldn't be classified. Thus, the sample was thus reduced
by about 40%. The smaller sample was problematic, as it limited the
ability to make balanced comparisons across outlets with varying article
counts. \
Additionally Some regression results produced very large standard
errors, which complicates the interpretation of statistical
significance. In certain cases, the classifications also defied
expectations. For instance, in Task 5 on constructed oppositions, it was
surprising to find left-leaning, pro-immigration outlets categorized as
constructing “us vs. them” narratives. This raises questions about
whether the task prompt may have been misunderstood or too vague.
Despite multiple rounds of prompt testing and refinement, the validation
of outputs was done manually and on a small sample, which may have left
some misclassifications undetected. \
Moreover, some categories may have been too broad, potentially reducing
nuance. In Task 3 (Framing), the political/legal frame was very
dominant, while the "no frame" category (0) was rarely used. This could
suggesting either overclassification or that the framing categories were
not sufficiently distinct. A similar issue could be seen in Task 4
(Sentiment), where neutral or concerned tones were most frequently
assigned, possibly indicating difficulty in differentiating between mild
evaluative language and true neutrality. \
Finally, the study was deliberately designed to only focus on periods
around major initiatives. This increases the salience, however excludes
regular reporting. It could be beneficial, to compare the discourse
during the initiatives with regular reporting periods.

# References {.unnumbered}

Eberl, J.-M., Meltzer, C. E., Heidenreich, T., Herrero, B., Lind, F., & Boomgaarden, H. G. (2018). The European media discourse on immigration and its effects: A Literature Review, Annals of the International Communication Association, 42(3), 207–223, https://doi.org/10.1080/23808985.2018.1497452

Entman, R. M. (1993). Framing: Toward Clarification of a Fractured Paradigm. Journal of Communication, 43(4), 51–58.

McCombs, M. E., & Shaw, D. L. (1972). The Agenda-Setting Function of Mass Media. Public Opinion Quarterly, 36(2), 176–187, https://doi.org/10.1086/267990

Nabi, R. L. (2003). Exploring the Framing Effects of Emotion: Do Discrete Emotions Differentially Influence Information Accessibility, Information Seeking, and Policy Preference? Communication Research, 30(2), 224-247. https://doi.org/10.1177/0093650202250881 

Spirig, J. (2024). Politicians, Newspapers, and Immigration Referendums: Exploring the Boundaries of Media Effects. Political Communication, 41(5), 786–807. https://doi.org/10.1080/10584609.2024.2321539

Strömbäck, J. (2008). Four Phases of Mediatization: An Analysis of the Mediatization of Politics. The International Journal of Press/Politics, 13(3), 228-246. https://doi.org/10.1177/1940161208319097 

# Appendix {.unnumbered}

## Original prompt for the GPT API

You are an expert in Swiss politics, political communication, and media
framing. You are highly familiar with how immigration debates are shaped
in the press. You will be provided with Swiss newspaper articles related
to immigration, published around the time of major initiatives
(Volksabstimmungen). Your task is to carefully analyze each article and
perform the following classification tasks, using the instructions
provided for each task.

**Task 1 - Relevance** Analyze whether this article is relevant for a
discourse analysis of immigration in the Swiss context. The article is
relevant if it discusses immigration as an issue in Switzerland. This
includes for example: immigration to Switzerland, Swiss political
debates about immigration or asylum, Swiss parties (e.g. SVP, SP) or
initiatives related to migration. Articles about immigration in other
countries are not relevant, unless the article explicitly connects them
to Swiss politics or society.

List of categories (return only the number in your final classification)
1: Relevant — the article discusses immigration in the Swiss context.

0: Not relevant — immigration is not discussed meaningfully, or only in
a foreign/non-Swiss context.

**Task 2 - Indirect Mention of Immigration** Detect whether immigration
is mentioned briefly or indirectly, and is not the main focus of the
article. For example, immigration may appear in only one sentence or
sub-paragraph, as part of a larger discussion on another topic (e.g.,
economy, housing).

List of categories (return only the number in your final classification)
1: Immigration is mentioned briefly or indirectly, but is not the main
topic.

0: Either immigration is not mentioned at all, or immigration is the
main topic.

**Task 3 - Framing of Immigration** Determine how immigration is framed
in the article. Each frame emphasizes certain aspects of immigration.
Only classify the frame the article itself uses. Do not assign a frame
just because the article quotes, summarizes, or describes what someone
else says — unless the article clearly endorses, reinforces, or builds
on that framing. If the article presents an argument but then debunks,
distances itself, or mockingly reports it, do not assign that frame.
Only assign a frame if that’s how the article itself presents
immigration. If multiple frames are present, chosoe the one that is most
apparent, dominant or frequently emphasized in the article. If no
framing of immigration is present, choose "0: Not applicable".

List of categories (return only the number in your final classification)
1: Economic frame. The article discusses immigration in terms of its
impact on the economy. This includes effects on jobs, labor force or
competition, welfare, or productivity. Migrants may be described as
workers, taxpayers, economic burdens, or financial contributors.

2: Cultural/Identity frame. The article frames immigration as a cultural
issue. The article focuses on immigration's effect on Swiss identity,
values, language, religion or traditions. Migrants may be portrayed as
culturally different or challenging to Swiss identity.

3: Security frame. The article frames immigration as a threat to public
safety or order. This includes mention of crime, terrorism, instability,
or uncontrolled borders. Migrants may be associated with risk and
insecurity.

4: Humanitarian frame. The article presents migrants as people in need
of help or protection. This frame emphasized suffering, vulnerability,
or moral responsibility.

5: Political/Legal frame. The article focuses on on immigration as a
legal or political issue. This includes laws, referendums, asylum
procedures, or EU policy. Debates about sovereignty, institutions, or
party positions also fall under this frame.

0: Not applicable.

Examples “Our economy depends on skilled foreign labor to fill critical
gaps.” Response: 1

“The SVP warns that immigration will destroy our national culture.”
Response: 0 (if not endorsed by the article) or 2 (if article reinforces
this message)

“Critics say migrants burden the social system — but the data proves
otherwise.” Response: 5

**Task 4 - Sentiment Toward Immigration** Assess the emotional tone used
when immigration or migrants are discussed in the article. Only evaluate
the sentiment expressed toward immigration or migrants themselves.Do not
classify emotional tone that is directed at political parties or actors,
the media, campaigns or general opinions.If the article mentions fear,
anger, or crisis, but is clearly critiquing, mocking, or distancing
itself from those claims, do not assign that sentiment. If multiple
sentiments are present, select the dominant or most consistent one. If
you can not detect a sentiment, choose "0: Not applicable".

List of categories (return only the number in your final classification)
1: Hopeful. This includes immigration being seen as an opportunity,
benefit, or positive force for society.

2: Sympathetic. This includes compassion for migrants or refugees, or
emphasizes suffering, vulnerability, or moral duty in the context of
immigration.

3: Neutral. The tone is strictly factual, descriptive, or statistical,
without clear emotional framing.

4: Concerned / Uncertain. This includes expression of unease, ambiguity,
or worry, but not in a strongly emotional or accusatory way. It
aknowledges problems, but without panic or blame.

5: Fearful. This includes portraying immigration as dangerous,
destabilizing, or threatening to public order, values, or safety.
Immigration is described as an imminent, generalized threat, usually
emotionally charged.

6: Angry. This includes blame, outrage, or emotionally charged criticism
— often targeting migrants, elites, or institutions, or immigrants
themselves.

7: Dismissive / Downplaying. This includes portraying immigration as
exaggerated, unimportant, or overblown.

0: Not applicable.

Examples "Mass immigration could overwhelm our system." Response: 5

“The SVP warns that mass immigration could destroy our values — a claim
widely debunked by experts.” Response: 7

“The rapid pace of immigration is putting real pressure on schools and
hospitals, and policymakers must act.” Response: 4

**Task 5 - Constructed Oppositions** Identify whether the article
constructs an opposition between "the Swiss" and migrants/foreigners.
Oppositions define who belongs and who does not by attributing
contrasting characteristics to in-groups and out-groups. This includes
both explicit and implicit contrasts. This includes ascribing positive
traits to "the Swiss", ascribing different or negative traits to
immigrants/foreigners or using comparative languages, stereotypes or
generalizations. Only classify an opposition as present if the article
constructs, reproduces or reinforces a contrast between "the Swiss" and
migrants/foreigners. Do not code 1 if the article quotes or describes
someone else’s oppositional framing but does not adopt it or critiques
it.

List of categories (return either "0" or "1" in your final
classification) 1: An opposition is present.

0: No opposition is present.

Examples “Unlike Swiss workers, many migrants lack basic
qualifications.” Response: 1

“Switzerland must preserve its values from outside influence.” Response:
1

“The SVP claims that foreigners threaten Swiss jobs — but this fear is
exaggerated and unsupported by evidence.” Response: 0

“Many believe immigrants don't share Swiss values, yet recent studies
show high integration success.” Response: 0

At the end of your answer, return only the selected number for each
task, in this exact format: 1 0 5 4 0

Do not include labels, descriptions, or any other text.

## R Code

```{r ref.label=knitr::all_labels()}
#| echo: true
#| eval: false

```
