---
title: "Title Data Essay"
subtitle: "Data mining project"
author: 
  - "Zoe von Allmen, zoe.vonallmen@stud.unilu.ch, 12-124-433"
  - "Supervisor: Dr. Andrea De Angelis"
date: today
date-format: "D. MMMM YYYY"
format: 
  pdf:
    documentclass: scrreprt
    number-sections: true
    toc: false
fontsize: 12pt
linestretch: 1.5
geometry: left=2.5cm,right=2.5cm,top=3cm,bottom=3cm
execute:
  echo: false
  warning: false
knitr:
  opts_chunk:
    message: false
editor: 
  markdown: 
    wrap: 72
---

# Introduction

This paper investigates how immigration is discussed in Swiss media,
specifically in the context of national initiatives and referendums.
Using large-scale newspaper data and employing large language models for
classification tasks, the project analyzes how immigration is framed,
the emotional tone applied to it, and whether oppositional constructions
("us" vs. "them") are present. It focuses media discourses during
moments when political stakes were especially high, which is, during
direct democratic votes, and examines how immigration is discussed by
ideologically differing newspapers.

Building on established literature, the basis of this project is the
assumption, that media plays an important role in the perception of
diverse issues. That is not only through what they cover, but how they
do so. through the use of certain linguistic concepts or the
accentuation of certain aspects. Prior research has shown that media
ownership and political orientation can influence the visibility and
framing of certain topics. In Western Europe, and Switzerland in
particular, immigration has become an increasingly salient and
politicized issue (Q). Over the past two decades, Switzerland has held
numerous initiatives and referendums directly addressing immigration,
such as for example the "Masseneinwanderungsinitiative" (Massimmigration
Initiative) in 2014 or the "Begrenzungsinitiative" (Restriction
Initiative) in 2020. Most recently, the "Swiss People's Party" (SVP)
launched a new initiative, called "Nachhaltigkeitsinitiative", which
again addresses the topic of Swiss immigration.

In a direct democratic country like Switzerland, media discourse is
particularly relevant. As the Swiss people vote directly on these
initiatives, public narratives, influenced by media consumption, can
influence perceptions of migrants and even possibly influence policy
support. This project further seeks to expand the discourse analysis by utilizing the recent advances in large language models to scale up what has traditionally been small-scale qualitative work. Features such as framing, sentiment, and opposition, which have often been identified manually before, are now extracted in a more
systematic and large-scale way.

In summary, this project aims to analyze media discourse of
ideologically different media outlets at times where immigration is
especially politicized and stakes are high - during the time of
initiatives. The study therefor tries to answer the following research
question: *How is immigration represented in Swiss media coverage during politically salient moments?* 

More precisely, the following sub-questions should be answered:

-   *What framing strategies and sentiments are used to define immigration and its implications in Swiss media during national initiatives?*

-   *To what extent are oppositions constructed or reinforced in immigration coverage*

-   *How does the use of these concepts vary across ideologically diverse newspapers?*

# Theory

The theoretical basis for this project include framing theory, political communication and media and the construction of oppositiional identities.
- Framing Theory, esp. in immigration (used for categorization)
- Agenda Setting, politicization, media ownership, media in direct dem. 
- Sentiments in Immigration (used for categorization)
- Identity costruction (immigration, media)


# Data & Method

**Article collection**

Relevant newspaper articles were collected via the Swissdox API, which provides
a wide range of Swiss news outlets. The sample collected contains only articles
written in the german language.

Selection criteria included:

- *Keyword filtering*: Articles were retrieved based on keyword searches intended
to capture wide range of immigration-related articles. The final list of keywords included: 
einwander* zuwander* asyl* flüchtling* Personenfreizügigkeit, überfremdung, migrationspolitik, migrationsabkommen, abschiebung, integrationspolitik
These kewords were selected after initial testing and revising of sample articles to minimize irrelevant results. 

- *Newspapers*: Seven major Swiss newspapers were selected to represent a range of ideological orientations: 
- Basler Zeitung (BAZ) - right wing after ownership changed in
2000? 
- Blick -  
- Wochenzeitung (WOZ): left-wing 
- Weltwoche (WEW): right wing 
- SRF: public boradcaster, politically neutral 
- Neue Zürcher Zeitung (NZZ): economically liberal/rather conservative
- Tagesanzeiger (TA) - centrist
Only print versions of each newspaper were used to avoid duplicates and ensure consistent article structure over time, as some articles were retrieved from the early 2000's. 

- *Time frames*: To focus on moments of increased politicization, four Swiss initiatives related to immigration were selected. For each initiative, a four week time period was defined, three weeks before and one week after the respective vote. The initiatives include the following: 
- "Initiative für eine Regelung der Zuwanderung" (Initiative for regulating immigration), vote on 24.09.2001, time frame: 2000-06-24 to: 2000-10-24
- "Initiative gege Masseneinwanderung" (Initiative against massimmigration), vote on 09.02.2014, time frame : 2013-11-09 to: 2014-03-09
- Initiative "Stop Überbevölkerung" (Stop overpopulation), vote on 30.11.2014, 
time frame: 2014-08-30 to: 2014-12-30
- "Begrenzungsinitiative" (Restriction initiative), vote on 27.09.2020, 
time frame: 2020-06-27 to: 2020-10-27

In total, the fina sample based on these filters contained 1731 articles.

**Classification via GPT API**

To analyze the articles, the OpenAI GPT-4.0 API was used to perform classification tasks. The classifications was based on a custom prompt that defined five separate tasks. Each article was sent into the model in full text, with a detailed instruction. The full version of the prompt can be found in the appendix. 

**Task Overview**
Each article was coded along five dimensions: 

- Task 1- Relevance: 
Binary classification: 
1: Relevant — the article discusses immigration in the Swiss context. 
0: Not relevant — immigration is not discussed meaningfully, or only in a 
foreign/non-Swiss context.

- Task 2 - Indirect Mention of Immigration 
Binary classification: 
1: Immigration is mentioned briefly or indirectly, but is not the main topic. 
0: Either immigration is not mentioned at all, or immigration is the main
topic.

- Task 3 - #Task 3 - Framing of Immigration 
1: Economic 
2: Cultural/Identity 
3: Security 
4: Humanitarian  
5: Political/Legal  
0: not applicable
In the final evaluation, categories 3 (security), 4 (humanitarian) and 0(not applicable) were collapsed into a new label "9 = other", due to their low frequency. 

- Task 4 - Sentiment Towards Immigration
1: Hopeful. 
2: Sympathetic. 
3: Neutral.
4: Concerned / Uncertain. 
5: Fearful. 
6: Angry.
7: Dismissive / Downplaying. 
For the analysis, due to the low frequencies of some frames, categories were recoded as follows: 
Sentiment 1 (hopeful) and sentiment 2 (sympathetic) were merged into
a category "8 - positive". 
Sentiments 5 (fearful), 7 (dismissive)
and 0 (not applicable) were collapsed into a new category "9 - other".

Task 5 - Constructed Opposition 
1: An opposition is present.
0: No opposition is present.

Each task included definitions, a more detailed explanation of the categories as well
as example sentences and categorizations. Further, the GPT model was instructed to  act as an expert on Swiss politics, political communication and media discourse.
Several test runs and prompt refinements based on the test runs were conducted before processing the full data set, to ensure the validity and consistency of the classification. For example, explanations were modified and examples
of edge cases were added. After multiple test runs and quality checks,
the full data set was processed. 

Categorization based on...

**Final Sample**:
Out of the initial 1731 articles, 706 could not be classified by the API. Of the remaining 1025 articles, the relevance task (Task 1) identified 772 articles as relevant for the research question. These 772 articles comprise the final data set which was used for the analysis. 

## Results
```{r}
library(tidyverse)
Joined_Data_filtered <- read_csv("Data/analysis_data_relevant_only.csv")
nrow(Joined_Data_filtered)

Joined_Data_filtered |> 
  select(medium_name) |> 
  map(table)
```
The final data set consists of 772 articles. This includes 169 articles of the Basler Zeitung (BAZ), 175 articles of the Tages-Anzeiger (TA), 172 articles of the Neue Zürcher Zeitung (NZZ), 124 articles of SRF, 68 articles of Blick, 53 articles of Die Weltwoche and 15 articles of the WOZ. 

**Analysis of frames**
```{r}
Joined_Data_filtered <- Joined_Data_filtered |>
  mutate(code_3_numeric = as.numeric(as.character(code_3))) |>
  mutate(task3_collapsed = case_when(
    code_3_numeric %in% c(0, 3, 4) ~ 9,
    TRUE ~ code_3_numeric
  ))

Joined_Data_filtered <- Joined_Data_filtered |>
  mutate(task3_collapsed = as.factor(task3_collapsed))

library(nnet)
m_frames_medium <- multinom(task3_collapsed ~ medium_name, data = Joined_Data_filtered)
summary(m_frames_medium)

```

To examine the newspaper's use of different frames a multinominal logictic regression was conducted, with the reference category economic frame (frame 1). Key results are as follows:
- Some outlets showed higher odds of using cultural frames over economic ones. For example, Die Wochenzeitung and Die Weltwoche had positive coefficients for this comparison (1.13 and 0.72 respectively), suggesting these outlets are more likely to frame immigration culturally than economically.
- SRF and Neue Zürcher Zeitung (NZZ) had positive coefficients, indicating they are more likely to use a political/legal frame than an economic one, particularly SRF (coefficient = 1.07).
- The model suggests a reasonable model fit (Residual Deviance = 1020.71, AIC = 1062.71), however standard errors for most coefficients are very large, which suggests that they may not be statistically significant. 

The following visualization shows the predicted probabilities of frames by newspaper.

```{r}
library(ggeffects)
pred_frame <- ggpredict(m_frames_medium, terms = "medium_name")

Pred_Frame <- plot(pred_frame) +
  ggtitle("Predicted Probabilities of Frame") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

print(Pred_Frame)
```
**Analysis of sentiment**

```{r}
Joined_Data_filtered |> 
  count(code_4)

Joined_Data_filtered |> 
  group_by(medium_name, code_3) |> 
  summarise(n = n()) |> 
  ungroup()

Joined_Data_filtered <- Joined_Data_filtered |>
  mutate(code_4_numeric = as.numeric(as.character(code_4))) |>
  mutate(task4_collapsed = case_when(
    code_4_numeric %in% c(1, 2) ~ 8, #hopeful & sympathetic => positive
    code_4_numeric %in% c(0, 5, 7) ~ 9, #not applicable, fearful, dismissive => other
    TRUE ~ code_4_numeric
  ))

Joined_Data_filtered <- Joined_Data_filtered |>
  mutate(task4_collapsed = as.factor(task4_collapsed))

m_sentiment_medium <- multinom(task4_collapsed ~ medium_name, data = Joined_Data_filtered)
summary(m_sentiment_medium)

#Predicted sentiment
library(ggeffects)
pred_sentiment <- ggpredict(m_sentiment_medium, terms = "medium_name")

Pred_Sentiment <- plot(pred_sentiment) +
  ggtitle("Predicted Probabilities of Sentiment") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

To assess how the newspapers differ in sentiment used when discussing immigration, a multinominal logistic regression was run, with sentiment type as outcome and media outlet as predictor. The neutral tone acts as reference category. Key results are as follows:
- Most media outlets did not show strong deviations from neutrality. However, Die Wochenzeitung had a positive coefficient (1.30), suggesting that compared to neutral tone, it was more likely to use a concerned tone. 
- Die Weltwoche and Die Wochenzeitung had relatively strong positive coefficients (1.42 and 2.20), suggesting these outlets may use more emotionally critical or accusatory language than others. SRF and NZZ, in contrast, had negative coefficients, indicating they were less likely to express anger relative to a neutral tone.
- Strong negative coefficients for Blick (–13.58) and Weltwoche (–12.48) indicate that positive sentiment was very unlikely in these outlets. Die Wochenzeitung stands out with a positive coefficient (2.31), indicating they used a rather hopeful or sympathetic tone.
- However, some sentiment categories were underrepresented in the data set, eading to extreme or unstable coefficiets for certain outlets. esults should be interpreted with caution. 

The following visualization shows the predicted probabilities of sentiment by newspaper.

```{r}
print(Pred_Sentiment)
```

**Analysis of constructed oppositions**

```{r}
Joined_Data_filtered |> 
  count(code_5)

Joined_Data_filtered |> 
  group_by(medium_name, code_5) |> 
  summarise(n = n()) |> 
  ungroup()

Joined_Data_filtered <- Joined_Data_filtered |> 
  mutate(code_5 = as.factor(code_5))

m_opposition_medium <- glm(code_5 ~ medium_name, 
                           data = Joined_Data_filtered, 
                           family = binomial)

summary(m_opposition_medium)

pred_opposition <- ggpredict(m_opposition_medium, terms = "medium_name")
Pred_Opposition <- plot(pred_opposition) +
  ggtitle("Predicted Probability of Constructed Opposition by Media Outlet") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

To examines the presence and variation of constructed oppositions, a binary logistic regression was run. Constructed opposition (code_5) acts as the dependent variable, the newspapers as the predictor. Some key results are as follows: 
- Die Weltwoche shows a significantly higher likelihood of constructing oppositions compared to the baseline (B = 1.10, p < 0.001), suggesting a stronger tendency to emphasize divides between "the Swiss" and migrants.
- Die Wochenzeitung also had a significantly higher probability (B = 1.27, p < 0.05), though this result should be interpreted cautiously due to a smaller sample size.
- In contrast, Neue Zürcher Zeitung was less likely to have oppositional framing present (B = -0.54, p = 0.049).
- The remaining outlets, including Blick, Tages-Anzeiger, and SRF, did not show statistically significant deviations from the baseline.

The following visualization shows the predicted probabilities of constructed opposition by newspaper.

```{r}
print(Pred_Opposition)
```

## Conclusion

This project examined how Swiss newspapers represent immigration in the context of politically salient moments, specifically during national initiatives and referendums. Based on the results of the analysis, the research questions are discussed and answered as follows. 
Political ad economic frames dominate the newspapers when it comes to immigration. Right-leaning newspapers, like Die Weltwoche, are more frequently employ opositional or cultural farmings, while liberal or centrist outlets(NZZ, SRF), focus on more on political or legal aspects. 
Emotional tone, overall, is mostly neutral or concerned, although there were traces of anger and dismissiveness found. The right-wing newspaper Die Weltwoche, for example, appears more likely to express an angry sentiment, while the left-wing newspaper Die Wochenzeitung uses positive sentiments. 
The use of constructed oppositions, "us vs. them", is not uniform across the media landscape, Die Weltwoche and Die Wochenzeitung showed higher likelihoods of constructing such contrasts. 
These findings suggest that even within a non-polarized media environment like Switzerland, ideological positioning influences how immigration is framed, especially during times of heightened public attention and direct democratic decision-making.

**Limitations**
Despite these insights, several limitations affect the generalizability and validity of the findings. First of all, the use of the LLM for for the article classification introduced some constraints. The classification of the articles resulted in a substantial proportion of articles that couldn't be classified. Thus, the sample was thus reduced by about 40%. The smaller sample was problematic, as it limited the ability to make balanced comparisons across outlets with varying article counts. 
Additionally Some regression results produced very large standard errors, which complicates the interpretation of statistical significance. In certain cases, the classifications also defied expectations. For instance, in Task 5 on constructed oppositions, it was surprising to find left-leaning, pro-immigration outlets categorized as constructing “us vs. them” narratives. This raises questions about whether the task prompt may have been misunderstood or too vague. Despite multiple rounds of prompt testing and refinement, the validation of outputs was done manually and on a small sample, which may have left some misclassifications undetected.
Moreover, some categories may have been too broad, potentially reducing nuance. In Task 3 (Framing), the political/legal frame was very dominant, while the "no frame" category (0) was rarely used. This could suggesting either overclassification or that the framing categories were not sufficiently distinct. A similar issue could be seen in Task 4 (Sentiment), where neutral or concerned tones were most frequently assigned, possibly indicating difficulty in differentiating between mild evaluative language and true neutrality.
Finally, the study was deliberately designed to only focus on periods around major initiatives. This increases the salience, however excludes regular reporting. It could be beneficial, to compare the discourse during the initiatives with regular reporting periods. 


# Bibliografie {.unnumbered}

# Appendix {.unnumbered}

- AGP prompt
- 

## R Code

```{r ref.label=knitr::all_labels()}
#| echo: true
#| eval: false

```
